What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2025-03-30 group-b/E2-analysis-calibration.Rmd

```{r message=FALSE}
library(jsonlite)
library(dplyr)
library(tidyr)
library(ggplot2)
library(patchwork)
library(lmerTest)
library(broom.mixed)
```

@@

@@

Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, averaging initial calibration (or re-calibration for participants who repeated calibration) and calibration at the halfway point. Calibration scores varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %). 
The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants (see Figure\ \@ref(fig:E2-calib-effect)).

>>>>

```{r message=FALSE}
library(jsonlite)
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(patchwork)
library(lmerTest)
library(broom.mixed)
```

@@

write_csv(calib.by.subj,"output/E2_calib_data_subj.csv") # for survey results analysis

@@

Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, averaging initial calibration (or re-calibration for participants who repeated calibration) and calibration at the halfway point. Calibration scores varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%). 
The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants (see Figure\ \@ref(fig:E2-calib-effect)).

### 2025-03-30 manuscript.Rmd

>>>>

This plug-in (and potentially other webcam-based eye-tracking options) opens the door to including a broader, more diverse sample of participants in cognitive science research. In contrast to the typical in-lab eye-tracking sample, which consists primarily of young university students from WEIRD countries [@henrich2010weirdest; @linxen2021weird; @de2023psychology; @rad2018toward], webcam eye-tracking can reach a much more diverse population, as the only prerequisite is access to a computer with a webcam (a standard feature on most modern laptops and tablets). While webcam eyetracking cannot by itself eliminate all demographic biases, some of which are in any case baked in by history [@henrich2020weirdest], it can help to reduce them, at least for studies amenable to the paradigm.
